%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Patricio Lopez Juri} % Your name at the top

\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'

\moveleft.5\hoffset\centerline{Santiago, Chile}
\moveleft.5\hoffset\centerline{+56 9 90511003}
\moveleft.5\hoffset\centerline{patricio@lopezjuri.com}
\moveleft.5\hoffset\centerline{https://lopezjuri.com}

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------

\section{ABOUT ME}

Software Engineering student and full-stack developer passionate in producing real solutions using the best tools available. Interested in \textit{state of the art} technology. Focused in high quality code and top-tier development/deployment procedures. Always up to date in news related to computer science, software engineering and information technologies. Enthusiastic in sharing and teaching the acquired knowledge.

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{EDUCATION}

{\sl Software Engineering,}  \hfill Match 2012 - Current \\
Pontifical Catholic University of Chile\\

%----------------------------------------------------------------------------------------
%	Technology SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{TECHNOLOGY \\ SKILLS}

{\sl Programming Languages:}  Python, C\#, Go, Java, Javascript, Typescript, Ruby, Objective-C, C. \\
{\sl Development:} Git, Code quality, Code review, Documentation, Unit testing. \\
{\sl Database:} Postgres, SQLite, MongoDB, Neo4J, Redis, Realm.io. \\
{\sl Backend:} Node.js, Express.js, Gin, Ruby on Rails, Sinatra, Flask. \\
{\sl Frontend:}  Angular.js, React.js, Polymer, jQuery, HTML, CSS. \\
{\sl Mobile:}   iOS, Android, Windows Phone, React-Native. \\
{\sl Desktop:}   .NET, Cross-platform, CLI. \\
{\sl Deployment:}   Ubuntu server, Microservices, Container-Based architecture, IaaS, PaaS, SaaS, Continuous integration, Server monitoring. \\
{\sl Other:}  Docker, nginx, Library and module development (npm, pypi, gems, cocoapods). \\

%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{EXPERIENCE}

{\sl Teaching Assistant} \hfill March 2015 - December 2015 \\
Web Technologies And Applications
\begin{itemize}  \itemsep -2pt
\item Ruby on Rails as the main framework.
\item Designed course architecture on top of Github.
\item Project reviewer and guide.
\end{itemize}

{\sl Head Teaching Assistant} \hfill March 2015 - December 2015 \\
Advanced Programming
\begin{itemize}  \itemsep -2pt
\item Course refactoring from C\# and SVN to Python and Git to fit current development tools and standards.
\item Setup of all Git repositories and their maintenance.
\item Designed course architecture on top of Github.
\item Development of administrative tools to automate repository administration.
\item Code reviewer of course material and activities.
\end{itemize}

{\sl Alma Mater UC } \hfill January 2014 - July 2014 \\
Mobile App Developer - Personal project
\begin{itemize}  \itemsep -2pt
\item Develop of the UC's unofficial mobile app for iOS and Android.
\item Research and implementation of how to integrate the university services.
\item Mapping of the majority of classrooms.
\item More than 15.000 downloads.
\end{itemize}

\end{resume}
\end{document}
