%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer}
    {ConsenSys.net}
    {Remote - Brooklyn, NY, USA}
    {Jan. 2018 - PRESENT}
    {
      \begin{cvitems}
        \item Architect of the \href{https://old.tokenfoundry.com/}{TokenFoundry.com} platform where we raise more than US\$30 million from the sales of Virtue Poker and FOAM tokens during 2018 in a legal and secure manner. Handled thousand of users and seamlessly incorporated the Ethereum blockchain to handle payments.
        \item Successfully integrated Know-Your-Costumer services into the platform to prevent money laundry and to blacklist politically exposed users.
        \item Implemented a versatile quiz system to prevent speculators from purchasing tokens.
        \item Built a flexible and smart React component library with styled-components and server-side rendering.
        \item {Successfully instructed and managed team and code-base to ensure a consistent code quality.}
        \item {Built software and systems that integrated with the Ethereum blockchain on the frontend and on the backend.}
        \item {Customized pip modules related to OAuth2 and its integration with Django 2.}
        \item Implemented a GraphQL API in a microservice-based architecture for \href{https://www.daisypayments.com}{DaisyPayments.com}. For asynchronous communication satisfactorily defined Kafka event format and standards.
        \item Designed and implemented an authentication and authorization system for public API and internal services.
      \end{cvitems}
    }
  
  \cventry
    {Adjunct Instructor Professor}
    {Pontifical Catholic University of Chile - Postgraduate School}
    {Santiago, Chile}
    {Aug. 2017 - Dec. 2017}
    {
      \begin{cvitems}
        \item {Imparting course: Technologies and Applications of the World Wide Web to 10 professional students.}
        \item {Designed from scratch a course with hands-on methodology using Ruby on Rails.}
        \item {Lessons about HTTP, business models and basics of web design.}
        \item {Recorded programming session about Ruby on Rails, HTML and CSS for the classroom.}
      \end{cvitems}
    }

  \cventry
    {Freelance Software Engineer}
    {ImpulsoDocente}
    {Santiago, Chile}
    {Jun. 2017 - Nov. 2017}
    {
      \begin{cvitems}
        \item {Design and implementation a mobile to help teachers improve their methodology through videos and feedback.}
        \item Built with React-Native, Redux and Ruby on Rails.
        \item {Addressed UI/UX concepts and taught product-management methods (Kanban) to clients.}
      \end{cvitems}
    }

  \cventry
    {Freelance Software Engineer}
    {FEUC (Federación de Estudiantes de la Universidad Católica de Chile)}
    {Santiago, Chile}
    {Jan. 2017 - Aug. 2017}
    {
      \begin{cvitems}
        \item {Lead the requirement gathering, design and implementation of a mobile app built with React-Native and Redux with a Express.js, Keystone.js and MongoDB backend.}
        \item Available at \url{https://github.com/open-source-uc/FEUC-mobile} and got arround 5000 downloads (iOS \& Android).
      \end{cvitems}
    }
    
  % \cventry
%     {Teaching Assistant (each class with around 30 students)}
%     {Pontifical Catholic University of Chile}
%     {Santiago, Chile}
%     {Aug. 2013 - Dec 2017}
%     {
%       \begin{cvitems}
%         \item {Mentor for the Major Field Capstone Project guides a team of to 10 last-year computer science students during the full development cycle of a software project: 2 semesters.}
%         \item {Software System Architecture: 1 semester.}
%         \item {Detailed Software Design: 1 semester.}
%         \item {Advanced Design of Web Applications: 1 semester.}
%         \item {Software Engineering: 1 semester.}
%         \item {Web Technologies and Applications: 2 semesters.}
%         \item {Advanced Programming: 5 semesters.}
%       \end{cvitems}
%     }
    
  \cventry
    {Freelance Software Engineer}
    {Booz cl}
    {Santiago, Chile}
    {Mar. 2017 - May. 2017}
    {
      \begin{cvitems}
        \item {Implement shopping cart and a search feature with Node.js, MongoDB and jQuery.}
        \item {Code refactoring caused several improvements such as increased overall speed and reduced client-side files size.}
      \end{cvitems}
    }
    
  \cventry
    {Egghead Instructor}
    {egghead.io}
    {Remote}
    {Mar. 2017 - PRESENT}
    {
      \begin{cvitems}
        \item {Prepare, record and edit an online video course about developing modern JSON WEB APIs with Koa and the latest JavaScript semantics. (Work in progress).}
      \end{cvitems}
    }
    
  \cventry
    {Software Engineer}
    {Mediastream SpA}
    {Santiago, Chile}
    {Dec. 2016 - Dec 2017}
    {
      \begin{cvitems}
        \item {Research about Functions as a Service (FaaS) and evaluate the project of splitting the main monolithic service built with Express.js and MongoDB to migrate to AWS Lambda and DynamoDB.}
        \item {Lead developer at the design and implementation a full-stack application with Koa, Amazon RDS, React, React-Native and Redux with shared code-base between mobile and web with i18n support.}
        \item {Prepare and evaluate technical interviews for senior candidates.}
        \item {Improve developer experience (DX) by setting a developer-friendly and debuggable environment.}
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }
    
  \cventry
    {Freelance Software Engineer}
    {Núcleo Milenio Centro de Investigación de la Web Semántica – CIWS}
    {Santiago, Chile}
    {Oct. 2016 - Oct. 2017}
    {
      \begin{cvitems}
        \item {Lead developer in charge of updating the official website to a new CMS in Node.js and MongoDB from Python and MySQL.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
